True versus apparent shapes of astrophysical bow shocks

### 2016-04-15 papers/Paper1/sec-application.tex
Work on Fig 7 caption and accompanying text

@@

This scenario can be described with the formalism of \citep{Canto:1996}, who proposes an algebraic solution for the two winds interaction problem in the thin shell approximation, in terms of a free parameter $\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$,
the winds momentum ratio, which the quantities with subindex 1 corresponds to the strongest wind, therefore $\beta<=1$.

If we apply the \citep{Canto:1996} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \citep{Canto:1996}
numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).

@@

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes obtained with the \citep{Canto:1996} algebraic formalism using (\ref{eq:nprop}) to describe the proplyd wind density. The distance are normalized with $D$
to avoid dependency with this parameter.}
\label{fig:r-beta}
\end{figure}

@@

In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \citep{Canto:1996}
and obtain the following relation:

@@

$R_0$ is obtained directly from equation (27) of \citep{Canto:1996} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \citep{Canto:1996} at $\theta=\frac{\pi}{2}$ we obtain the following:

@@

\begin{figure*}
\begin{tabular}{ccc}
\includegraphics[width=0.35\linewidth]{R0-b}&
\includegraphics[width=0.35\linewidth]{Rc-b} &
\includegraphics[width=0.35\linewidth]{R90-b}
\end{tabular}
\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \citep{Canto:1996}
are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
\label{fig:rad-beta}
\end{figure*}

>>>>

\defcitealias{Canto:1996}{CRW}
\newcommand\CRW{\citetalias{Canto:1996}}

@@

This scenario can be described with the formalism of
\citet[][hereafter \CRW{}]{Canto:1996}, who proposes an algebraic
solution for the two winds interaction problem in the thin shell
approximation, in terms of a free parameter
$\beta\equiv\frac{\dot{M}_wv_w}{\dot{M}_{w1}v_{w1}}$, the winds
momentum ratio, which the quantities with subindex 1 corresponds to
the strongest wind, therefore $\beta<=1$.

If we apply the \CRW{} formalism for a photoevaporated flow with density given by (\ref{eq:nprop}), we find that the solutions for equations (8) - (11) of \citep{Canto:1996} are the following:

\begin{align}
\dot{M}_w &= \frac{\dot{M}_w^0}{3}\left(1-\cos^{3/2}\theta\right) \label{eq:dotprop} \\
\dot{\Pi}_z &= \frac{1}{5}v_w \dot{M}_w^0\left(1-\cos^{5/2}\theta\right)  \label{eq:pir}\\
\dot{\Pi}_r &= \frac{1}{2}v_w\dot{M}_w^0\left(\frac{4}{5}E\left(\frac{\theta}{2}|2\right) - \frac{1}{5}\sin 2\theta\cos^{1/2}\theta\right) \label{eq:piz}\\
\dot{J}_w = 0 \label{eq:jdot}
\end{align}  
The solution for (\ref{eq:piz}) includes an incomplete elliptic integral of the second kind. Combining equations  (\ref{eq:dotprop}) to (\ref{eq:jdot}) with equation (6) of \CRW{}
numerically in python code, we can obtain the bow shock shape $R(\theta)$, as illustred in figure (\ref{fig:r-beta}).

@@

\begin{figure}
\includegraphics[width=\linewidth]{r-beta}
\caption{Bow shock shapes for interacting winds in the thin-shell
  approximation. Coordinates are normalized by $D$, the distance
  between the two wind sources.  The weaker source is at \((0.0, 0.0)\)
  and the stronger source is at \((1.0, 0.0)\).  Results are shown for
  different values of the wind momentum ratio, \(\beta\), and for the
  case where the weaker wind is isotropic (dashed lines) or an
  anisotropic proplyd photoevaporation flow (solid lines).}
\label{fig:r-beta}
\end{figure}

@@

In order to find an analytic form of the characteristic radii $(R_0,R_c,R_{90})$, we may combine equations (\ref{eq:dotprop}) to (\ref{eq:jdot}) with (6) and (23) from \CRW{}
and obtain the following relation:

@@

$R_0$ is obtained directly from equation (27) of \CRW{} as the distance from the inner source where the RAM pressure of the interacting winds is in equilibrium.

We can obtain $R_{90}$ by the following process:
Evaluating equations  (\ref{eq:th1th}) and (23) from \CRW{} at $\theta=\frac{\pi}{2}$ we obtain the following:

@@

\begin{figure*}
\begin{tabular}{ccc}
\includegraphics[width=0.35\linewidth]{R0-b}&
\includegraphics[width=0.35\linewidth]{Rc-b} &
\includegraphics[width=0.35\linewidth]{R90-b}
\end{tabular}
\caption{$R_0$, $R_c$ and $R_{90}$ versus $\beta$ for a fixed set of inclinations. Equations (\ref{eq:r90}), (\ref{eq:Rcurv}), and (27) from \CRW{}
are labeled as ``analytic i=0''. Note that the analytic solution deviates from the numeric solution when $\beta \gtrsim 0.1$}
\label{fig:rad-beta}
\end{figure*}
